### 2024-10-23 Scripts/Manuscript/manuscript.Rmd
clean-up before uploading pre-print.

---
title             : "Assessing Reliable and Valid Measurement for Informative Replications in Psychology"
shorttitle        : "Measurement and Informative Replications"

author: 
  - name          : "Goos, Cas"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Professor Cobbenhagenlaan 125, 5037 DB, Tilburg, The Netherlands"
    email         : "c.goos@tilburguniversity.edu"

  - name          : "Bakker, Marjan"
    affiliation   : "1"

  - name          : "Wicherts, Jelte M."
    affiliation   : "1"

  - name          : "Nuijten, Michèle B."
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Tilburg University"

authornote: |
  1 Department of Methodology and Statistics, Tilburg School of Social and Behavioral Sciences, Tilburg University, Tilburg, NL.

  The authors made the following contributions. CG: Conceptualization, Data curation, Formal Analysis, Investigation, Methodology, Project Administration, Software, Visualization, Writing - Original Draft Preparation, Writing - Review & Editing; MB: Conceptualization, Supervision, Writing - Review & Editing; JW: Conceptualization, Supervision, Writing - Review & Editing; MN: Conceptualization, Project Administration, Supervision, Validation, Writing - Review & Editing.

@@

keywords          : "reliability, construct validity, measurement, reporting, questionable measurement practices, replicability, credibility, psychology"
wordcount         : "159"

@@

    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-\z@\relax}%
      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
    \makeatother

@@

classoption       : "man"
output            : papaja::apa6_pdf
knit              : worcs::cite_all
---

@@

Unfortunately, the Reproducibility Project: Psychology [RPP\; @osc2015estimating] and other large-scale replication projects that sought to replicate earlier and seminal findings [@klein2014investigating; @ebersole2016many; @klein2018many; @klein2022many; @ebersole2020many] typically yielded smaller effects in replications compared to original studies, with Many-Labs projects featuring different locations and samples. In response to this string of failed replications, there was widespread alarm regarding the credibility and robustness of findings in psychological science [@hughes2018psychology; @giner2019crisis], and efforts to explain the low replication rate. The factors that have been proposed include questionable research practices [@simmons2011false; @john2012measuring; @cumming2014new; @wicherts2016degrees], questionable reporting practices [@bakker2011mis; @nuijten2016prevalence], and biased publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science]. Another important factor is the impact of measurement-related challenges on replicability and credibility.

@@

Replicability and reliable and valid measurement are essential elements of the credibility of a finding, and are related to each other. Indeed, recent studies have illustrated that both the reliability of the measure [@stanley2014expectations] and the reporting of information relevant to demonstrating the validity of the measurement [@shaw2020measurement; @flake2017construct; @flake2020measurement] may predict the replicability of psychological findings.

@@

@flake2022construct documented QMPs among 100 replications and their respective original articles from the RPP [@osc2015estimating]. They coded the number of measures, the number of items in the measure, and the information that was reported describing the measure and providing evidence justifying its use. Besides limited reporting of validity and reliability evidence for the coded measures, @flake2022construct found that several of the measures in the RPP did not report the number of items, the response format, or the scoring of the scale. Furthermore, only eight of the 40 translated scales contained validity evidence for the translated version of the scale. Measures were similarly modified between original and replication in other ways without evidence showing that the modification did not invalidate the measurement.

@@

Measurement reliability can vary across samples, because the residual variance or the true variance in the item scores, or both, differs between samples. While differences in these variances across samples is inevitable, these differences should not be systematic between replication and original samples for their results to remain comparable. Therefore, we investigated the reliability in replication (Research Question 1a; RQ1a ) and original psychological research (RQ1b). The Many Labs studies were intended as direct replications, which implies that deviations from the original research should be irrelevant for testing the effect [@nosek2022replicability], including systematic differences in reliability (Hypothesis 1; H1).

@@

We conceptually replicate the findings on measurement reporting of @flake2022construct by documenting the frequency of QMPs in replications of psychological research (RQ4a) and original psychological research (RQ4b). @flake2022construct found that RPP replications averaged more QMPs than original studies. We hypothesized that for our Many Labs sample, QMPs would be more frequent in original psychological research than in replication research (H4), because the Many Labs replications used structured protocols documenting the measurement.

QMPs obscure information about a particular measurement, which may cause issues reconstructing that measurement in subsequent replication attempts. Because resulting deviations in measurement may be partly responsible for deviations in replication and original effects [@flake2022construct], we investigated whether QMPs in replication protocols were associated with the replication outcome (RQ5). A reduction in QMPs corresponds to greater transparency in measurement reporting. In line with earlier research finding that other transparency-related practices are associated with more robust estimates of effects [@wicherts2011willingness; @protzko2020high], we expected QMPs in replications to be negatively associated with replication success (H5).

@flake2022construct proposed that QMPs in original articles may impede recreating measurements for replications, and indeed @shaw2020measurement found evidence for such a spill-over effect for validity. In line with this research, we investigated the association between QMPs in original research and QMPs in replications of psychological research (RQ6). We expected the total number of QMPs in original psychological research to be positively related to the total number of QMPs in replication research (H6).

@@

We used the published reports of the Many Labs projects [@klein2014investigating; @ebersole2016many; @ebersole2020many; @klein2018many]) to determine replication success based on the reported significance of the meta-analytic effect. An effect was considered successfully replicated if the meta-analytic effect was in the same direction as the original effect and had a p-value lower than .05.

@@

Table \@ref(tab:ReplicationNrTable) shows the number of replication sets, measures, and measures per study, as well as the proportion of successful replications, for each of the Many Labs separately and in total.

@@

Because each replication was nested within one of four Many Labs projects, our data had a multilevel structure. Furthermore, `r sum(data_h456_replications$appearance != 1)` replications used more than one primary measure, resulting in `r nrow(data_h456_replications)` measures in both `r sum(data_h456_replications$appearance == 1)` replications protocols and `r sum(coded_data_original$appearance == 1)` original articles[^2]. Of these `r nrow(data_h456_replications)` measures `r sum(data_h456_replications$mod_check == "True")` were modified from the original to the replication[^3]. In the replications, the data of responses on the measures was further nested in several labs per replication. The combined sample size of all labs in the replications was on average `r round(mean(data_h456_replications[data_h456_replications$appearance == 1]$N), 0)`, which was approximately `r round(mean(data_h456_replications[data_h456_replications$appearance == 1]$N) / mean(data_h456_original[data_h456_original$appearance == 1 & !is.na(data_h456_original$N),]$N), 0)` times larger than the average in original studies, which were conducted in single labs.

[^3]: For 7 measures the number of items were modified from the original article to the replication. To check whether or not this had a confounding impact on our results, we re-ran the analyses testing the hypotheses excluding data from these studies (see [Supplementary Analyses E](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_item_reduced_measures_analyses.Rmd)). We found that removing these measures’ data had minimal impact on the overall results. Therefore, the results presented below were based on data from all the measures.

@@

Figure \@ref(fig:Plot23AlphaCode) displays the estimates of tau, which indicates the differences in true reliability scores between labs for a given measure. For `r sum(data_h23_avg$QEp > .05)` measures, the tau estimate was not significantly different from 0, while the true variation in reliability across labs was significant for `r apa_num(sum(data_h23_avg$QEp <= .05), numerals = FALSE)` measures. The true reliability was quite variable for some measures. For instance, the estimate of the standard deviation of the true reliability of the top measure in the graph (a measure of conscientiousness from @gosling2003very used in the replication of @defruyt2000cloninger) equaled `r apa_num(data_h23_avg$tau[data_h23_avg$g == "De Fruyt et al. (2000)"], digits = 3, gt1 = FALSE)` points of Cronbach’s Alpha.

@@

Figure \@ref(fig:ReliabilityReportingFlowDiagram) depicts the flow of measures in relation to reliability reporting. First, it shows that almost half of the measures in both replication (N = `r apa_num(sum(data_h456_replications$N_items == "1 item measure"))`) and original research (N = `r apa_num(sum(data_h456_original$N_items == "1 item measure"))`) were single-item measures. When looking at the multiple-item measures, the graph illustrates that r N_reported_reliabilities_replications` measures in the replication protocols (`r apa_num((as.numeric(N_reported_reliabilities_replications_number_style) / sum(data_h456_replications$N_items != "1 item measure")) * 100, digits = 1)` \%) and `r N_reported_reliabilities_original` measures in the original articles (`r apa_num((as.numeric(N_reported_reliabilities_original) / sum(data_h456_original$N_items != "1 item measure")) * 100, digits = 1)` \%) reported a reliability coefficient. The most commonly reported reliability coefficient was Cronbach’s Alpha, which accounted for `r apa_num(sum(data_h456_replications$reliability_type == "alpha"), numerals = FALSE)` reported reliabilities in the replication protocols, and `r apa_num(sum(data_h456_original$reliability_type == "alpha"))` in the original articles.

@@

```{r ReportingInformation, include = FALSE}
## first some descriptives of reliability reporting
# we get these descriptives from the combination of both replication and original
# QMP data.
reporting_data <- rbind(data_h456_original, data_h456_replications)

@@

Reliability was more commonly reported in original (N = `r N_reported_reliabilities_original`; `r apa_num((as.numeric(N_reported_reliabilities_original) / nrow(data_h456_original)) * 100, digits = 1)` \%) as compared to replication research = `r N_reported_reliabilities_replications_number_style`; `r apa_num((as.numeric(N_reported_reliabilities_replications_number_style) / nrow(data_h456_replications)) * 100, digits = 1)` \%), $\chi^{2}$(`r apa_num(reliability_reporting_test_result$parameter)`) = `r apa_num(reliability_reporting_test_result$statistic)`, *p* = `r apa_p(reliability_reporting_test_result$p.value)`. Validity evidence was similarly reported infrequently. Validity evidence from a factor analysis was reported in `r apa_num(sum(data_h456_original$sel_psychometric_evidence_REV != "None" & data_h456_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` original articles, while in only `r apa_num(sum(data_h456_replications$sel_psychometric_evidence_REV != "None" & data_h456_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` replications. This difference was not significant, however the total number of factor analyses reported was low  ($\chi^{2}$(`r apa_num(factor_reporting_test_result$parameter)`) = `r apa_num(factor_reporting_test_result$statistic)`, *p* = `r apa_p(factor_reporting_test_result$p.value)`).

@@

Overall, the QMP ratios (i.e., the ratio of the total number of measurement practices that were not transparently and fully reported on) were low in both original and replication studies. The top part of Figure \@ref(fig:Plot456Code) displays the distributions of the total QMP ratio for both original articles and replication protocols, showing that the average QMP ratio in replication protocols was smaller (`r apa_num(Mean_Rat_Rep)`) than in original articles (`r apa_num(Mean_Rat_Org)`). The bottom of Figure \@ref(fig:Plot456Code) displays the observed QMP ratios per QMP type for both original articles and replication protocols, showing that original articles tended to contain fewer Definition QMPs, but more selection and operationalization QMPS, with Quantification QMPs being comparable. The number of measures that were modified also differed between original and replication. In total `r QMP_NA_percentage` of all responses across all QMP items were non-applicable.

@@

# re-ordering the QMP-types, because it didn't save
plot_456_data$QMP_type <- factor(plot_456_data$QMP_type, levels = c("Definition", "Selection", "Operationalization", "Quantification", "Modification", "Total"))

@@

@@

@stanley2014expectations illustrated that measurement error, when not attenuated for, can impact replication assessments. However, we observed no relation between reliability and replicability. This result also runs counter to the fact that according to statistical theory, the increased noise in the data implied by lower reliability decreases the effect size estimates based on those data. However, the relationship between reliability and replicability is complex [@willson1980research; @lebreton2014corrections; @oswald2015Imperfect; @zhang2024Metaanalysis]. Combined with the fact that we could only calculate reliability for a small number of measures meant we had low statistical power to detect the overall relation between reliability and replicability, which provides the most likely explanation for our non-significant findings.

@@

Third, the replication protocols were written before data were collected, which means no measurement based on these protocols had not taken place yet. As a result, no data were available yet from which the replicating researchers could have calculated reliability and validity. This would explain why there was little reliability and validity evidence reported in replication protocols. It may still represent a problem, however, because original articles similarly rarely reported evidence on reliability and validity. This implies that the replications commonly picked measures for which validity could not be checked.

@@

However, it is worth noting that the spillover effect was only observed for QMPs coded with the revised coding protocol. Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol (see [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.Rmd for results based on the initial protocol). Furthermore, these hypotheses were supported by only one of the multilevel models. However, these models were limited in group and sample size, leading to results that are somewhat uncertain.

@@

Our study had several limitations. We encountered Including challenges we encountered in operationalizing QMPs. Whereas previous research has focused on descriptives of specific QMPs detrimental to construct validity [@flake2022construct; @shaw2020measurement], we combined all coded QMPs together as an index to assess measurement practices and evaluate their impact on replicability. However, this also means that it remains uncertain if our operationalization accurately captured the concept. We encountered particular difficulty in determining when a practice is questionable, and the impact of the context on this decision. As a result, we already deemed it necessary to revise our coding protocol to be more lenient regarding more context dependent QMPs compared to the initial protocol. This revision was not trivial, as it altered the interpretation of our results. This finding reflects the challenges in operationalizing QMPs in a single index.

Another challenge in constructing one overarching QMP variable was how to quantify it.. We constructed ratios to cancel out the effects of non-applicable items. However, this has the consequence that both a measure for which all relevant measurement-related information was reported, and a measure for which no item was applicable would have a QMP ratio of zero. Yet, we would not consider the latter case to indicate the same level of completeness as the first. A little more than one-third of all responses were not applicable. As a result, the relation between QMP ratios and measurement reporting completeness may have been obscured to some extent. Additionally, it is not obvious from observing a QMP ratio whether good research practices were clearly violated. One might argue that any QMP is a sign of questionable research making any ratio greater than zero problematic. However, not all violations may have detrimental consequences or are relevant in all contexts.

These challenges are potential threats to the validity of our assessment of QMPs. To assess the validity of QMP measurement, construct validity would not be appropriate as QMPs are no latent construct. Instead, validity can be evaluated based on the extent to which a measured QMP score can be used to predict other variables it is expected to be associated with. For this future research will be needed to develop a framework of the associations between QMPs and other variables, and then test whether measured QMP scores are associated with those variables. To develop this framework, researchers can use this study and earlier studies by @shaw2020measurement and @flake2022construct. To improve upon previous measures, the criteria on measurement reporting as set out in the @aera2014standards can be used as an additional source.

A second limitation is that some of our tests were likely underpowered. Especially the tests on reliability, because of the small number of reported reliabilities, and multiple item scales with available data. However, this limitation also illustrates two key findings. One finding is that reliability was rarely reported for measures in both original articles and replication protocols. The other finding is that around half of the measures in our sample were single-item measures. The use of single-item measures comes with psychometric risks [@diamantopoulos2012guidelines; @nunnally1978overview] and is more limited with respect to the type of reliability and validity evidence that can be determined [@sarstedt2016selecting; @shaw2020measurement]. Because of these issues, it could even be argued that using single-item measures is a QMP in certain contexts.

@@

Finally, we note that we used an observational design meaning that we cannot attach definitive causal directions to the relations observed in this study. To directly assess if there is a negative impact of reliability and QMPs on replicability, we would need experimental research. Future research could for example randomly assign original studies in a large-scale replication project to either needing to report all relevant measurement information as noted down in Table 1 in @flake2020measurement, while other studies receive no such reporting requirements. Similarly, the requirement to use validated measures based on the criteria set out in Sections 1, 2, and 3 in the @aera2014standards standards, or lack thereof could be randomly assigned to conditions. Although such experimental designs would be the most direct way to assess causality, it would take tremendous coordination and funding to integrate original studies into a large-scale replication project from the start. While such efforts are not unprecedented [@protzko2020high], alternative methods also exist to assess causal relations on observational data, at least to some extent. @rohrer2018thinking has suggested researchers make use of Directed Acyclic Graphs to investigate causality in (non-)experimental settings by systematically accounting for confounding influences on an effect.

@@

Taking all the findings together, we formulated several recommendations. First, reliable and valid measures are a prerequisite for credible findings. The observation that many measures are not reported with such evidence is worrying because it obscures the credibility of findings and hampers scientific progress. Therefore, we join earlier recommendations [@hogan2004empirical; @barry2014validity; @flake2020measurement; @flake2022construct] that establishing evidence for the validity of scales should become a community standard for credible research. Furthermore, reliability coefficient estimates for multiple-item scales should, by default, always be reported since these estimates can readily be obtained with most statistical software and provide important information on a measure’s performance. Only researchers who can provide reasoning to the contrary for their research should be exempt from this default.

>>>>

---
title             : "Assessing Reliable and Valid Measurement as a Prerequisite for Informative Replications in Psychology"
shorttitle        : "Measurement and Informative Replications"

author: 
  - name          : Cas Goos
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Professor Cobbenhagenlaan 125, 5037 DB, Tilburg, The Netherlands"
    email         : "c.goos@tilburguniversity.edu"

  - name          : Marjan Bakker
    affiliation   : "1"

  - name          : Jelte M. Wicherts
    affiliation   : "1"

  - name          : Michèle B. Nuijten
    affiliation   : "1"

authornote: |
  The authors made the following contributions. CG: Conceptualization, Data curation, Formal Analysis, Investigation, Methodology, Project Administration, Software, Visualization, Writing - Original Draft Preparation, Writing - Review & Editing; MB: Conceptualization, Supervision, Writing - Review & Editing; JW: Conceptualization, Supervision, Writing - Review & Editing; MN: Conceptualization, Project Administration, Supervision, Validation, Writing - Review & Editing.

@@

keywords          : "reliability, construct validity, measurement, reporting, questionable measurement practices, replicability, credibility, psychology"
wordcount         : "158"

@@

    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-\z@\relax}%
      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
    \makeatother
  - \renewcommand\author[1]{}
  - \renewcommand\affiliation[1]{}
  - \authorsnames[1, 1, 1, 1]{Cas Goos, Marjan Bakker, Jelte M. Wicherts, Michèle B. Nuijten}
  - \authorsaffiliations{{Department of Methodology and Statistics, Tilburg School of Social and Behavioral Sciences, Tilburg University, Tilburg, NL.}}

@@

classoption       : man
output            : papaja::apa6_pdf
knit              : worcs::cite_all
---

@@

Unfortunately, the Reproducibility Project: Psychology [RPP\; @osc2015estimating] and other large-scale replication projects that sought to replicate earlier and seminal findings [@klein2014investigating; @ebersole2016many; @klein2018many; @klein2022many; @ebersole2020many] typically yielded smaller effects in replications compared to original studies, with Many-Labs projects featuring different locations and samples. In response to this string of failed replications, there was widespread alarm regarding the credibility and robustness of findings in psychological science [@hughes2018psychology; @giner2019crisis], combined with efforts to explain the low replication rate. The factors that have been proposed include questionable research practices [@simmons2011false; @john2012measuring; @cumming2014new; @wicherts2016degrees], questionable reporting practices [@bakker2011mis; @nuijten2016prevalence], and biased publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science]. Another important factor is the impact of measurement-related challenges on replicability and credibility.

@@

Replicability and reliable and valid measurement are essential to the credibility of a finding, and are related to each other. Indeed, recent studies have illustrated that both the reliability of the measure [@stanley2014expectations] and the reporting of information relevant to demonstrating the validity of the measurement [@shaw2020measurement; @flake2017construct; @flake2020measurement] may predict the replicability of psychological findings.

@@

@flake2022construct documented QMPs among 100 replications and their respective original articles from the RPP [@osc2015estimating]. They coded the number of measures, the number of items in the measure, and the information that was reported describing the measure and providing evidence justifying its use. Besides limited reporting of validity and reliability evidence for the coded measures, @flake2022construct found that several of the measures in the RPP did not report the number of items, the response format, or the scoring of the scale. Furthermore, only eight of the 40 translated scales contained validity evidence for the translated version of the scale. Evidence showing that this and other modifications between original and replication did not invalidate the measurement was rarely reported.

@@

Measurement reliability can vary across samples, because the residual variance or the true variance in the item scores, or both, differs between samples. While differences in these variances across samples is inevitable, these differences should not be systematic between replication and original samples for their results to remain comparable. Therefore, we investigated the reliability in replication (Research Question 1a; RQ1a[^1]) and original psychological research (RQ1b). The Many Labs studies were intended as direct replications, which implies that deviations from the original research should be irrelevant for testing the effect [@nosek2022replicability], including systematic differences in reliability (Hypothesis 1; H1).

@@

We conceptually replicate the findings on measurement reporting of @flake2022construct by documenting the frequency of QMPs in replications of psychological research (RQ4a) and original psychological research (RQ4b). @flake2022construct found that RPP replications contained on average more QMPs than original studies. We hypothesized that for our Many Labs sample, QMPs would be more frequent in original psychological research than in replication research (H4), because the Many Labs replications used structured protocols documenting the measurement.

QMPs obscure information about a particular measurement, which may cause issues when reconstructing that measurement in subsequent replication attempts. Because resulting deviations in measurement may be partly responsible for deviations in replication and original effects [@flake2022construct], we investigated whether QMPs in replication protocols were associated with the replication outcome (RQ5). A reduction in QMPs corresponds to greater transparency in measurement reporting. In line with earlier research finding that other transparency-related practices are associated with more robust estimates of effects [@wicherts2011willingness], we expected QMPs in replications to be negatively associated with replication success (H5).

@flake2022construct proposed that QMPs in original articles may impede recreating measurements for replications, and indeed @shaw2020measurement found evidence for such a spill-over effect with validity. In line with this research, we investigated the association between QMPs in original research and QMPs in replications of psychological research (RQ6). We expected the total number of QMPs in original psychological research to be positively related to the total number of QMPs in replication research (H6).

@@

We used the published reports of the Many Labs projects [@klein2014investigating; @ebersole2016many; @ebersole2020many; @klein2018many] to determine replication success based on the reported significance of the meta-analytic effect. An effect was considered successfully replicated if the meta-analytic effect was in the same direction as the original effect and had a p-value lower than .05.

@@

Table \@ref(tab:ReplicationNrTable) shows the number of replication sets, measures, and measures per study, as well as the proportion of successful replications, for each of the Many Labs separately and in total. Because each replication was nested within one of four Many Labs projects, our data had a multilevel structure. Furthermore, `r sum(data_h456_replications$appearance != 1)` replications used more than one primary measure, resulting in `r nrow(data_h456_replications)` measures in both `r sum(data_h456_replications$appearance == 1)` replications protocols and `r sum(coded_data_original$appearance == 1)` original articles[^2]. Of these `r nrow(data_h456_replications)` measures `r sum(data_h456_replications$mod_check == "True")` were modified from the original to the replication[^3]. In the replications, the data of responses on the measures was further nested in several labs per replication. The combined sample size of all labs in the replications was on average `r round(mean(data_h456_replications[data_h456_replications$appearance == 1]$N), 0)`, which was approximately `r round(mean(data_h456_replications[data_h456_replications$appearance == 1]$N) / mean(data_h456_original[data_h456_original$appearance == 1 & !is.na(data_h456_original$N),]$N), 0)` times larger than the average in original studies, which were conducted in single labs.

[^3]: For 7 measures the number of items were modified from the original article to the replication. To check whether or not this had a confounding impact on our results, we re-ran the analyses testing the hypotheses excluding data from these studies (see [Supplementary Analyses E](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_item_reduced_measures_analyses.Rmd)). We found that removing these measures’ data had minimal impact on the overall results. Therefore, the results presented below are based on data from all the measures.

@@

@@

Figure \@ref(fig:Plot23AlphaCode) displays the estimates of tau, which indicates the differences in true reliability scores between labs for a given measure. For `r sum(data_h23_avg$QEp > .05)` measures, the tau estimate was not significantly different from 0, meaning the true variation in reliability across labs was not significant. However, for the other `r apa_num(sum(data_h23_avg$QEp <= .05), numerals = FALSE)` measures the true reliability was quite variable. For instance, the estimate of the standard deviation of the true reliability of the top measure in the graph (a measure of conscientiousness from @gosling2003very used in the replication of @defruyt2000cloninger) equaled `r apa_num(data_h23_avg$tau[data_h23_avg$g == "De Fruyt et al. (2000)"], digits = 3, gt1 = FALSE)` points of Cronbach’s Alpha.

@@

Figure \@ref(fig:ReliabilityReportingFlowDiagram) depicts the flow of measures in relation to reliability reporting. First, it shows that almost half of the measures in both replication (N = `r apa_num(sum(data_h456_replications$N_items == "1 item measure"))`) and original research (N = `r apa_num(sum(data_h456_original$N_items == "1 item measure"))`) were single-item measures. When looking at the multiple-item measures, the graph illustrates that `r N_reported_reliabilities_replications` measures in the replication protocols (`r apa_num((as.numeric(N_reported_reliabilities_replications_number_style) / sum(data_h456_replications$N_items != "1 item measure")) * 100, digits = 1)` \%) and `r N_reported_reliabilities_original` measures in the original articles (`r apa_num((as.numeric(N_reported_reliabilities_original) / sum(data_h456_original$N_items != "1 item measure")) * 100, digits = 1)` \%) reported a reliability coefficient. The most commonly reported reliability coefficient was Cronbach’s Alpha, which accounted for `r apa_num(sum(data_h456_replications$reliability_type == "alpha"), numerals = FALSE)` reported reliabilities in the replication protocols, and `r apa_num(sum(data_h456_original$reliability_type == "alpha"))` in the original articles.

@@

```{r ReportingInformation, include = FALSE}
## first some descriptives of reliability reporting
# we get these descriptives from the combination of both replication and original
# QMP data.

reporting_data <- rbind(data_h456_original, data_h456_replications)

@@

Reliability was more commonly reported in original (N = `r N_reported_reliabilities_original`; `r apa_num((as.numeric(N_reported_reliabilities_original) / nrow(data_h456_original)) * 100, digits = 1)` \%) as compared to replication research (N = `r N_reported_reliabilities_replications_number_style`; `r apa_num((as.numeric(N_reported_reliabilities_replications_number_style) / nrow(data_h456_replications)) * 100, digits = 1)` \%, $\chi^{2}$(`r apa_num(reliability_reporting_test_result$parameter)`) = `r apa_num(reliability_reporting_test_result$statistic)`, *p* = `r apa_p(reliability_reporting_test_result$p.value)`). Validity evidence was similarly reported infrequently. Validity evidence from a factor analysis was reported in `r apa_num(sum(data_h456_original$sel_psychometric_evidence_REV != "None" & data_h456_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` original articles, while in only `r apa_num(sum(data_h456_replications$sel_psychometric_evidence_REV != "None" & data_h456_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` replications. This difference was not significant ($\chi^{2}$(`r apa_num(factor_reporting_test_result$parameter)`) = `r apa_num(factor_reporting_test_result$statistic)`, *p* = `r apa_p(factor_reporting_test_result$p.value)`), however the total number of factor analyses reported was low.

@@

Overall, the QMP ratios (i.e., the ratio of the total number of measurement practices that were not transparently and fully reported on) were low in both original and replication studies. The top part of Figure \@ref(fig:Plot456Code) displays the distributions of the total QMP ratio for both original articles and replication protocols, showing that the average QMP ratio in replication protocols was smaller (`r apa_num(Mean_Rat_Rep)`) than in original articles (`r apa_num(Mean_Rat_Org)`). The bottom of Figure \@ref(fig:Plot456Code) displays the observed QMP ratios per QMP type for both original articles and replication protocols, showing that original articles tended to contain fewer Definition QMPs, but more selection and operationalization QMPs, with Quantification QMPs being comparable. The number of measures that were modified also differed between original and replication. In total `r QMP_NA_percentage` of all responses across all QMP items were non-applicable.

@@

# re-ordering the QMP-types, because it didn't save
plot_456_data$QMP_type <- factor(plot_456_data$QMP_type, levels = c("Definition", "Selection", "Operationalisation", "Quantification", "Modification", "Total"))

@@

## Code for exporting figures to high resolution PNGs.
# png("manuscript_files/figure-self-export/plot_46_revised.png", width=1800, height=1200, res=300)
## #PLACE FIGURE CODE HERE#
# dev.off()
```

@@

@stanley2014expectations illustrated that measurement error, when not attenuated for, can impact replication assessments. However, we did not observe a relation between reliability and replicability. This result also runs counter to the fact that according to statistical theory, the increased noise in the data implied by lower reliability decreases the effect size estimates based on those data. However, the relationship between reliability and replicability is complex [@willson1980research; @lebreton2014corrections; @oswald2015Imperfect; @zhang2024Metaanalysis]. Combined with the fact that we could only calculate reliability for a small number of measures meant we had low statistical power to detect the overall relation between reliability and replicability, which provides the most likely explanation for our non-significant findings.

@@

Third, the replication protocols were written before data were collected, which means measurement based on these protocols had not taken place yet. As a result, no data were available yet from which the replicating researchers could have calculated reliability and validity. This would explain why there was little reliability and validity evidence reported in replication protocols. It may still represent a problem, however, because original articles similarly rarely reported evidence on reliability and validity. This implies that the replications commonly picked measures for which reliability and validity could not be checked.

@@

However, it is worth noting that the spillover effect was only observed for QMPs coded with the revised coding protocol. Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol (see [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.Rmd for results based on the initial protocol). Furthermore, these hypotheses were supported by only one of the multilevel models. These were limited in group and sample size however, making their results uncertain.

@@

Our study had several limitations. We encountered challenges in operationalizing QMPs. Whereas previous research has focused on descriptives of specific QMPs detrimental to construct validity [@flake2022construct; @shaw2020measurement], we combined all coded QMPs together as an index to assess measurement practices and evaluate their impact on replicability. However, this also means that it remains uncertain if our operationalization accurately captured the concept. We encountered particular difficulty in determining when a practice is questionable, and the impact of the context on this decision. As a result, we already deemed it necessary to revise our coding protocol to be more lenient regarding more context dependent QMPs compared to the initial protocol. This revision was not trivial, as it altered the interpretation of our results. This finding reflects the challenges in operationalizing QMPs in a single index.

Another challenge in constructing one overarching QMP variable was how to quantify it. We constructed ratios to cancel out the effects of non-applicable items. However, this has the consequence that both a measure for which all relevant measurement-related information was reported, and a measure for which no item was applicable would have a QMP ratio of zero. Yet, we would not consider the latter case to indicate the same level of completeness as the first. A little more than one-third of all responses were not applicable. As a result, the relation between QMP ratios and measurement reporting completeness may have been obscured to some extent. Additionally, it is not obvious from observing a QMP ratio whether good research practices were clearly violated. One might argue that any QMP is a sign of questionable research making any ratio greater than zero problematic. However, not all violations may have detrimental consequences or be relevant in all contexts.

These challenges are potential threats to the validity of our assessment of QMPs. The validity of QMPS could be evaluated based on the extent to which a measured QMP score can be used to predict other variables it is expected to be associated with. For this future research will be needed to develop a framework of the associations between QMPs and other variables, and then test whether measured QMP scores are associated with those variables. To develop this framework, researchers can use this study and earlier studies by @shaw2020measurement and @flake2022construct. To improve upon previous measures of QMPs, the criteria on measurement reporting as set out in the @aera2014standards can be used as an additional source.

A second limitation is that some of our tests were likely underpowered. Especially the tests on reliability, because of the small number of reported reliabilities and multiple item scales with available data. However, this limitation also illustrates two key findings. One finding is that reliability was rarely reported for measures in both original articles and replication protocols. The other finding is that around half of the measures in our sample were single-item measures. The use of single-item measures comes with psychometric risks [@diamantopoulos2012guidelines; @nunnally1978overview] and is more limited with respect to the type of reliability and validity evidence that can be determined [@sarstedt2016selecting; @shaw2020measurement]. Because of these issues, it could even be argued that using single-item measures is a QMP in certain contexts.

@@

Finally, we note that we used an observational design meaning that we cannot attach definitive causal directions to the relations observed in this study. To directly assess if there is a negative impact of reliability and QMPs on replicability, we would need experimental research. Future research could for example randomly assign original studies in a large-scale replication project to either needing to report all relevant measurement information as noted down in Table 1 in @flake2020measurement, while other studies receive no such reporting requirements. Similarly, the requirement to use validated measures based on the criteria set out in Sections 1, 2, and 3 in the @aera2014standards standards, or lack thereof could be randomly assigned to conditions. Although such experimental designs would be the most direct way to assess causality, it would take tremendous coordination and funding to integrate original studies into a large-scale replication project from the start. Alternative methods exist to assess causal relations on observational data, at least to some extent. @rohrer2018thinking has suggested researchers make use of Directed Acyclic Graphs to investigate causality in (non-)experimental settings by systematically accounting for confounding influences on an effect.

@@

Taking all the findings together, we formulated several recommendations. First, reliable and valid measures are a prerequisite for credible findings. The observation that many measures are not reported with such evidence is worrying because it obscures the credibility of findings and hampers scientific progress. Therefore, we join earlier recommendations [@hogan2004empirical; @barry2014validity; @flake2020measurement; @flake2022construct] that establishing evidence for the validity of scales should become a community standard for credible research. Furthermore, reliability coefficient estimates for multiple-item scales of a single construct should, by default, always be reported since these estimates can readily be obtained with most statistical software and provide important information on a measure’s performance. Only researchers who can provide reasoning to the contrary for their research should be exempt from this default.
